### 2024-08-29 paper.tex
start on fixing linalg

\begin{lemma}\label{nilpotent_centralizer}
    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix},\]
    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
\end{lemma}
\begin{proof}
    Let 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix}.\]
    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
    \par We have 
    \[J(\lambda)M = \begin{pmatrix}
        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
        \vdots & & \vdots\\
        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
        \vdots & & \vdots\\
        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
    \end{pmatrix}.\]
    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
\end{proof}
For nilpotent \(X\) in Jordan form and \(a\) in `normalized' form (i.e., with at most one nonzero element, which is a one), we will find the centralizer of \(A_{X, a, b}\) in 
\[\{(A, I) : A \in \gl_m\} \subseteq \gl_{m + n}.\]
Note that an element of the form \((A, I)\) commutes with \(A_{X, a, b}\) if and only if \(A\) commutes with \(X\), and \(aA = a\), and \(Ab = b\).
So, we just have to find 
\[\{A \in \gl_m : AX = XA, aA = a, Ab = b\}.\]

It is just the set of \(A = [A_{ij}]_{ij}\), where each \(A_{ij}\) is lower-left-Toeplitz.
\par Let \(v_{ij}\) be the leftmost column of \(A_{ij}\), so that
\[A_{ij} = \begin{pmatrix}
    v_{ij} \downshift 0 & \cdots & v_{ij} \downshift [\lambda_j - 1]
\end{pmatrix}.\]
Since \(A_{ij}\) is lower-left-Toeplitz, \(v_{ij}\) is of the form 
\[v_{ij} = \begin{pmatrix}
    0\\
    v_{ij}'
\end{pmatrix},\]
where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) can be chosen freely.
Now we determine which matrices of this form satisfy \(aA = a\).
For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
\par In the case that \(a = 0\), clearly every \(A\) works.
Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
This just requires that for each \(j\), we must have 
\[v_{ij} = \begin{pmatrix}
    0\\
    v_{ij}'
\end{pmatrix},\]
where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
So, we have now found the set 
\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
    0\\
    v_{ij}'
\end{pmatrix},\]
where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).

>>>>

\begin{lemma}\label{nilpotent_centralizer}
    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
    The centralizer of \(J(\lambda)\) in \(\gl_m\) is the subalgebra consisting of matrices 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix},\]
    where each \(M_{ij}\) is a \(\lambda_i \times \lambda_j\) matrix, such that each \(M_{ij}\) is lower-left Toeplitz.
\end{lemma}
\begin{proof}
    Let 
    \[M = \begin{pmatrix}
        M_{11} & \cdots & M_{1k}\\
        \vdots &        & \vdots\\
        M_{k1} & \cdots & M_{kk}
    \end{pmatrix}.\]
    We need to show that \(J(\lambda)M = MJ(\lambda)\) if and only if each \(M_{ij}\) is lower-left Toeplitz.
    \par We have 
    \[J(\lambda)M = \begin{pmatrix}
        J_{\lambda_1}M_{11} & \cdots & J_{\lambda_1}M_{1k}\\
        \vdots & & \vdots\\
        J_{\lambda_k}M_{k1} & \cdots & J_{\lambda_k}M_{kk}
    \end{pmatrix}, \textrm{ and } MJ(\lambda) = \begin{pmatrix}
        M_{11} J_{\lambda_1} & \cdots & M_{1k} J_{\lambda_k}\\
        \vdots & & \vdots\\
        M_{k1} J_{\lambda_1} & \cdots & M_{kk} J_{\lambda_k}
    \end{pmatrix}.\]
    So, we have \(J(\lambda)M = MJ(\lambda)\) if and only if \(\forall i,j. \; J_{\lambda_i} M_{ij} = M_{ij} J_{\lambda_j}\).
    Multiplying on the left by \(J_{\lambda_i}\) just shifts each row down by one, and multiplying on the right by \(J_{\lambda_j}\) shifts each column left by one.
    The matrices for which left-shifting gives the same result as down-shifting are exactly the lower-left Toeplitz matrices.
\end{proof}

\begin{lemma}
    Let \(\lambda = (\lambda_1, ..., \lambda_k)\) be a partition of \(m\).
    Let \(w \in \{1, ..., k\}\) and \(r \in \{1, ..., \lambda_w\}\).
    The set of \(M \in \mathfrak{z}_{\gl_m}(J(\lambda))\) such that \(aM = a\) 
\end{lemma}
Now we determine which matrices of this form satisfy \(aA = a\).
For simplicity, we will instead find the matrices \(A\) such that \(aA = 0\) (so that \(a(A + I) = a\)).
(Note that \(I \in C_1\), and \(C_1\) is closed under addition, so this is really the same thing.)
\par In the case that \(a = 0\), clearly every \(A\) works.
Otherwise, let \(i_0, j_0\) be such that \(a_{i_0,j_0} = 1\).
Now, clearly the constraint that \(aA = 0\) is just saying that the \((i_0,j_0)\)th row of \(A\) must be zero.
That is, for each \(j\) the \(j_0\)th row of \(A_{i_0j}\) must be zero.
This just requires that for each \(j\), we must have 
\[v_{ij} = \begin{pmatrix}
    0\\
    v_{ij}'
\end{pmatrix},\]
where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) can be chosen freely.
So, we have now found the set 
\[C_2 := \{A \in \gl_m : AX = XA, aA = a\}.\]
It is the matrices of the form \(I + A\), where \(A_{ij}\) is a block matrix of size \(\lambda_i \times \lambda_j\) with 
\[A_{ij} = T(v_{ij}) = T\begin{pmatrix}
    0\\
    v_{ij}'
\end{pmatrix},\]
where \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i, \lambda_j)}\) in the case \(i \neq i_0\) and \(v_{ij}' \in \mathbb{C}^{\min(\lambda_i - j_0, \lambda_j)}\) if \(i = i_0\).
